Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media

### 2017-12-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\title{ Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}

@@

\cortext[cor1]{Corresponding author.}
\address[UoA]{Fluids \& Structures Group, School of Engineering, University of Aberdeen, UK}
\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}

>>>>

\title{ Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media}%. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}

@@

\cortext[cor1]{Corresponding author.}
\address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
